Case study validations of automatic bullet matching

### 2018-09-28 index.Rmd
link to fsi

```{r, echo=FALSE, results = 'hide', warning = FALSE, message = FALSE}
features <- read.csv("data/fsi-features.csv")
features <- features %>% mutate(
  bullet1 = gsub("ullet ","", bullet1),
  bullet2 = gsub("ullet ","", bullet2)
)
b12 <- features %>% filter(group1 == "G1", barrel1=="KA", bullet1== "B1",
                           group2 == "G1", barrel2=="KA", bullet2== "B2")
p1 <- b12 %>% ggplot(aes(x = land1, y = land2, fill = rfscore)) + 
  geom_tile() + ggtitle ("Same barrel") +  
  scale_fill_gradient2("RF score: ", midpoint=0.3, low = "darkgrey", high = "darkorange", limits=c(0,1)) +
  theme_bw() + 
  xlab ("Bullet 2") + ylab("Bullet 1") +
  theme(legend.position = "bottom") + coord_equal()

@@

```{r hou, fig.width=9, fig.height = 3, fig.cap="Overview of matching scores for all pairs of questioned bullets to known bullets from five barrels (on the left) and questioned bullets to themselves (tiles on the right).", fig.subcap=c("Set 1", "Set 2", "Set 3"), fig.align="middle", fig.ncol=1}
features <- read.csv("data/fsi-features.csv")

>>>>

```{r, echo=FALSE, results = 'hide', warning = FALSE, message = FALSE}
features <- read.csv("data/fsi-features.csv.gz")
features <- features %>% mutate(
  bullet1 = gsub("ullet ","", bullet1),
  bullet2 = gsub("ullet ","", bullet2)
)
b12 <- features %>% filter(group1 == "G1", barrel1=="KA", bullet1== "B1",
                           group2 == "G1", barrel2=="KA", bullet2== "B2")
p1 <- b12 %>% ggplot(aes(x = land1, y = land2, fill = rfscore)) + 
  geom_tile() + ggtitle ("Same barrel") +  
  scale_fill_gradient2("RF score: ", midpoint=0.3, low = "darkgrey", high = "darkorange", limits=c(0,1)) +
  theme_bw() + 
  xlab ("Bullet 2") + ylab("Bullet 1") +
  theme(legend.position = "bottom") + coord_equal()

@@

```{r hou, fig.width=9, fig.height = 3, fig.cap="Overview of matching scores for all pairs of questioned bullets to known bullets from five barrels (on the left) and questioned bullets to themselves (tiles on the right).", fig.subcap=c("Set 1", "Set 2", "Set 3"), fig.align="middle", fig.ncol=1}
features <- read.csv("data/fsi-features.csv.gz")
